---
title: "IL DOA-EPA facilities matching"
author: "Zarrin Ali"
output: html_document
date: "2024-08-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(
  here, tidyverse, rlist,
  measurements #to convert coordinates from 'deg min sec' to decimal degrees
)
select <- dplyr::select
options(readr.show_col_types = FALSE) # suppress read_csv info
options(dplyr.summarise.inform = FALSE) # suppress summarize info
library(readxl)
```

This code was written by me when I was working as an RA for Professor Eyal Frank at Harris School of Public Policy in UChicago.

This script cleans, deduplicates, and merges Animal Feeding Operation (AFO) records in Illinois from two state agencies, the Department of Agriculture (DOA) and the Environmental Protection Agency (EPA), to create a unified, geocoded facility-level dataset.

Main steps: 
1. DOA internal matching: 
  - Splits the raw DOA dataset into records with and without facility IDs.
  - Uses fuzzy string matching on facility names to identify potential duplicates.
  - Filters matches by county and animal type, applies a similarity threshold, and reviews results manually in Excel as needed.
  - Creates a cleaned, unique facility-level dataset with consolidated coordinates and ownership information.
2. DOA–EPA cross-agency matching: 
  - Fuzzy-joins DOA and EPA datasets by facility name, filters by same county, and groups matches by string similarity.
  - Calculates geographic distances between matched facility coordinates to confirm validity.
  - Conducts manual verification in Excel for ambiguous cases.
  - Merges confirmed matches and appends unmatched DOA and EPA facilities to preserve full coverage.
3. Final dataset 
  - Collapses the merged dataset so that each facility corresponds to one row, consolidating similar facility and owner names using string distance metrics.
  - Ensures each unique facility has one consistent ID, name, address, and set of coordinates.

# Within DOA matching

```{r}
# Load dataset
raw_IL_DOA_2 <- read_csv("/Users/zarrinali/Documents/AFOs_IL/dataRAW_Zarrin/raw_IL-DOA-2.csv")

file_path <- "/Users/zarrinali/Documents/AFOs_IL/dataINTERM_Zarrin/Within-DOA matching"
```

```{r}
# Split into those to match (have no id) and those to be matched (have an id)
DOA_no_id <- raw_IL_DOA_2 %>%
  filter(is.na(id_operation_DOA)) %>%
  select(name_owner, name_facility, animalTypes, address, county, lat_plss, lon_plss, lat_raw, lon_raw, AUs)

DOA_with_id <- raw_IL_DOA_2 %>%
  filter(!is.na(id_operation_DOA)) %>%
  select(id_operation_DOA, name_owner, name_facility, animalTypes, address, county, lat_plss, lon_plss, lat_raw, lon_raw, AUs)

# Fuzzy-join by string distance of name_facility
matches_raw <- fuzzyjoin::stringdist_join(
  x = DOA_no_id,
  y = DOA_with_id,
  by = "name_facility",
  method = 'cosine',
  max_dist = 10,
  mode = 'left', # left join includes all rows from DOA_no_id and matched rows from DOA_with_id
  ignore_case = T,
  distance_col = "distance" # store the string distances
)

matches_raw <- matches_raw %>%
  select(name_facility.x, name_facility.y, distance, name_owner.x, name_owner.y, address.x, address.y, id_operation_DOA, county.x, county.y, animalTypes.x, animalTypes.y, everything())

# Filter: drop very bad matches and keep 5 best matches -> drop matches for which county and animal type dont match then keep 5 best matches
matches_filtered <- matches_raw %>%
  filter(county.x==county.y) %>% # Filter out matches that are not in the same county
  filter(animalTypes.x==animalTypes.y) %>%
  select(-county.y, -animalTypes.y) %>%
  rename(county = county.x, animalTypes = animalTypes.x) %>%
  group_by(name_facility.x) %>%
  arrange(distance) %>%
  filter(row_number()<=5) %>%
  select(name_facility.x, name_facility.y, distance, name_owner.x, name_owner.y, address.x, address.y, id_operation_DOA, everything())

# Simplifying dataset for determining threshold
matches_filtered_1 <- matches_filtered %>% 
  filter(distance != 0)
  
# Determining the threshold: determine in such a way that for all facilities under that threshold the smallest dist is the best match.

# Group 1: High quality matches
matched_gp1 <- matches_filtered %>%
  filter(distance < 0.1) %>% # The threshold chosen is 0.1
  group_by(name_facility.x) %>%
  filter(distance==min(distance)) %>% ungroup 

# Group 2: Remaining matches 
matched_gp2 <- matches_filtered %>%
  anti_join(matched_gp1 %>% select(name_facility.x), by = "name_facility.x") %>% # Excludes facility names already in the first group
  arrange(name_facility.x, distance) # Groups same faciliy names together and arranges by distance

# Saving datasets to view in Excel
write.csv(matched_gp1, file.path(file_path, "matched_gp1.csv"), row.names = FALSE)
write.csv(matched_gp2, file.path(file_path, "matched_gp2.csv"), row.names = FALSE)
write.csv(matches_raw, file.path(file_path, "matches_raw.csv"), row.names = FALSE)

# Process so far: divided the doa dataset into two: {those to match (have no id); those to be matched with (have an id)} and then did a fuzzymatch using name_facility. After skimming through the dataset and some deliberation (to make sure the following makes sense), filtered out the matches that have different counties and different animal types and kept the 5 best matches for each facility. Then took a threshold of 0.1 such that for all facilities under that threshold the smallest dist is the best match. Grouped the matches into two: (1) for dist < 0.1, the match with the smallest dist was kept, (2) for all other facility names, the top 5 matches with smallest dist are kept. Both datasets will be eventually collapsed to facility-by-name-by-name-owner level (so each facility will correspond to multiple rows if facility name/name owner are different).

# Reviewed matched_gp2 in Excel to keep the best match. For some facilities, the 5 matches with the smallest dist do not contain the best name match so searched for the best match in matches_raw (removed matches with diff county and animal type to streamline the search in matches_raw).

# Next steps: The data is divided into many groups and each group is individually reviewed and collapsed to the facility-by-name-by-name-owner level. Each following code chunk corresponds to one such group
```

## Group 1, part 1: Matches for which name_facility.x = name_facility.y (i.e., dist = 0)

```{r}
# Reminder: columns with .x suffix corresponds to the entries with no id_operation_DOA and columns with .y corresponds to entries with id_operation_DOA 

# Filtering to keep records for which name_facility.x = name_facility.y
matched_gp1_filtered <- matched_gp1 %>%  
  filter(distance == 0) # Only 10/1840 rows in matched_gp1 have dist > 0 so will deal with them separately

# Gather the .x and .y columns into long format where 1 row corresponds to the .x columns and the next row corresponds to the .y column
long_gp1 <- matched_gp1_filtered %>% 
  pivot_longer(
    cols = ends_with(c(".x", ".y")),
    names_to = c(".value", "source"),
    names_pattern = "(.*)\\.(x|y)"
  )

# Remove duplicate rows
long_gp1_filt <- long_gp1 %>%
  select(name_facility, name_owner, id_operation_DOA, county, animalTypes, address , lat_plss, lon_plss, lat_raw, lon_raw) %>%
  distinct() 

# Create the unique facility-level identifier by unique name_facility (Obviously, the same name_facility may refer to multiple facilities and multiple name_facilities may actually refer to 1 facility, so this column is subject to many changes as I sort through the data in Excel)
collapsed_gp1 <- long_gp1_filt %>% 
  group_by(name_facility) %>%
  mutate(my_Id_facility_doa = paste0("ildoa_", cur_group_id())) %>%
  ungroup() %>%
  arrange(name_facility, my_Id_facility_doa) %>%
  select(name_facility, name_owner, my_Id_facility_doa, everything()) 

# Saving the dataset for review in Excel
write.csv(collapsed_gp1, file.path(file_path, "collapsed_gp1.csv"), row.names = FALSE)

# Next steps: After reviewing collapsed_gp1 the 1st time (saved as collapsed_gp1_edited), will review some specific cases and then update the existing dataset

# 1st edited version from Excel
collapsed_gp1_edited<- read_csv(file.path(file_path, "collapsed_gp1_edited.csv"))

# Case 1: reviewing entries for which name_facility is different but id_operation_DOA is same
test_1 <- collapsed_gp1_edited %>%
  group_by(id_operation_DOA) %>%
  filter(n_distinct(name_facility) > 1) %>%
  ungroup() %>%
  arrange(id_operation_DOA)
write.csv(test_1, file.path(file_path, "diff_name_same_id_doa.csv"), row.names = FALSE)


# 2nd edited version from Excel after integrating case 1
collapsed_gp1_edited_2 <- read_csv(file.path(file_path, "collapsed_gp1_edited_2.csv"))

# Case 2: reviewing entries for which unique identifier (my_Id_facility_doa) is different but id_operation_DOA
test_2 <- collapsed_gp1_edited_2 %>%
  group_by(id_operation_DOA) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() %>%
  arrange(id_operation_DOA)
write.csv(test_2, file.path(file_path, "diff_uniqueid_same_id_doa.csv"), row.names = FALSE)

# 3rd edited version from Excel after integrating case 2
collapsed_gp1_edited_3 <- read_csv(file.path(file_path, "collapsed_gp1_edited_3.csv"))

# Case 3: reviewing entries with same unique identifier (my_Id_facility_doa) but diff id_operation_DOA
test_3 <- collapsed_gp1_edited_3 %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(id_operation_DOA) > 1) %>%
  ungroup() %>%
  arrange(my_Id_facility_doa)
write.csv(test_3, file.path(file_path, "diff_id_doa_same_uniqueid.csv"), row.names = FALSE)
        
# Final edited version from Excel after integrating case 1, 2 and 3
collapsed_gp1_edited_4 <- read_csv(file.path(file_path, "collapsed_gp1_edited_4.csv"))
```

## Group 1, part 2: Matches for which 0 \< dist \< 0.1 (i.e., entries in matched_gp1 with dist \> 0)

```{r}
matched_gp1_filtered_2 <- matched_gp1 %>%  
  filter(distance != 0) # Only 10 such entries

#Gather the .x and .y columns into long format
long_gp1_pt2 <- matched_gp1_filtered_2 %>% 
  pivot_longer(
    cols = ends_with(c(".x", ".y")),
    names_to = c(".value", "source"),
    names_pattern = "(.*)\\.(x|y)"
  ) %>% select(name_facility, name_owner, id_operation_DOA, county, animalTypes, address , lat_plss, lon_plss, lat_raw, lon_raw)

# Create the unique facility-level identifier (fixed later in Excel)
collapsed_gp1_pt2 <- long_gp1_pt2 %>% 
  group_by(name_facility) %>%
  mutate(my_Id_facility_doa = paste0("ildoa_", cur_group_id())) %>%
  ungroup() %>%
  arrange(name_facility, my_Id_facility_doa) %>%
  select(name_facility, name_owner, my_Id_facility_doa, everything()) 

# Saving the dataset for review in Excel
write.csv(collapsed_gp1_pt2, file.path(file_path, "collapsed_gp1_pt2.csv"), row.names = FALSE)

# Final edited version from Excel
collapsed_gp1_pt2_edited <- read_csv(file.path(file_path, "collapsed_gp1_pt2_edited.csv"))
```

## Group 2: Low quality matches (i.e., entries in matched_gp2)

```{r}
# Reviewed matched_gp2 in Excel and saved as matched_gp2_pt1_edited (had confusion about some facilities so sent them to Claire for matching)
matched_gp2_pt1_edited <- read_csv(file.path(file_path, "matched_gp2_pt1_edited.csv"))
matched_gp2_pt1_edited <- matched_gp2_pt1_edited %>%
  filter(rowSums(is.na(.)) != ncol(.)) # Remove rows with NA in all columns

#G ather the .x and .y columns into long format
long_gp2_pt1 <- matched_gp2_pt1_edited %>% 
  pivot_longer(
    cols = ends_with(c(".x", ".y")),
    names_to = c(".value", "source"),
    names_pattern = "(.*)\\.(x|y)"
  ) %>% select(name_facility, name_owner, id_operation_DOA, county, animalTypes, address , lat_plss, lon_plss, lat_raw, lon_raw) %>% distinct()
  
# Create the unique facility-level identifier (fixed later in Excel)
collapsed_gp2_pt1 <- long_gp2_pt1 %>% 
  group_by(name_facility) %>%
  mutate(my_Id_facility_doa = paste0("ildoa_", cur_group_id())) %>%
  ungroup() %>%
  arrange(id_operation_DOA) %>%
  select(name_facility, name_owner, my_Id_facility_doa, everything()) 

# Saving the dataset for review in Excel
write.csv(collapsed_gp2_pt1, file.path(file_path, "collapsed_gp2_pt1.csv"), row.names = FALSE)

# Final edited version from Excel (including the facilities that Claire matched)
collapsed_gp2_edited <- read_csv(file.path(file_path, "collapsed_gp2_edited.csv"))

```

```{r}
# Combined doa dataset from groups 1 and 2
doa_final_gp1_gp2 <- rbind(collapsed_gp1_edited_4, collapsed_gp1_pt2_edited, collapsed_gp2_edited)
write.csv(doa_final_gp1_gp2, file.path(file_path, "doa_final_gp1_gp2.csv"), row.names = FALSE)

```

## Group 4: Remaining facilities, i.e., facilities (based on name_facility) not in doa_final_gp1_gp2 but in raw_IL_DOA_2

```{r}
# Filter rows where name_facility in raw_IL_DOA_2 is not in doa_final_gp1_gp2 (and save for review in Excel)
gp_4 <- raw_IL_DOA_2 %>% 
  filter(!name_facility %in% doa_final_gp1_gp2$name_facility) %>% 
  select(name_facility, name_owner, id_operation_DOA, county, animalTypes, address , lat_plss, lon_plss, lat_raw, lon_raw)
write.csv(gp_4, file.path(file_path, "gp_4"), row.names = FALSE)

# Case A: filter those from gp_4 for which id_operation_DOA is in gp_4 AND doa_final_gp1_gp2 
gp_4_a <- gp_4 %>%
  filter(id_operation_DOA %in% doa_final_gp1_gp2$id_operation_DOA) # Filter rows where id_operation_DOA is in both gp_4 and doa_final_gp1_gp2

# Case B: also filter those entries in gp_4 where id_operation_DOA is NA
gp_4_na_id_doa <- gp_4 %>%
  filter(is.na(id_operation_DOA)) 

# Combine Case A and B and save for review in Excel
gp_4_filtered <- bind_rows(gp_4_a, gp_4_na_id_doa) %>% 
  arrange(name_facility)
write.csv(gp_4_filtered, file.path(file_path, "gp_4_filtered.csv"), row.names = FALSE)

# Sorted through gp_4_filtered on Excel and added entries to doa_final_gp1_gp2_gp4

# Case C: entries that are in gp_4 but not gp_4_filtered (and save for review in Excel)
gp_4_rest <- anti_join(gp_4, gp_4_filtered) %>%
  arrange(id_operation_DOA) %>% distinct()
write.csv(gp_4_rest, file.path(file_path, "gp_4_rest.csv"), row.names = FALSE)

# Final edited version from Excel with cases A, B and C integrated
doa_final_gp1_gp2_gp4 <- read_csv(file.path(file_path, "doa_final_gp1_gp2_gp4.csv"))
```

## Group 5: Facilities for where name_facility is NA

```{r}
# Approach: This group is divided into several parts for easier data wrangling

DOA_no_name_facility <- raw_IL_DOA_2 %>%
  filter(is.na(name_facility))
```

### Group 5.1: Those observations where same name_owner appears twice

```{r}
occ_2_name_owner <- DOA_no_name_facility %>%
  group_by(name_owner) %>%
  filter(n() == 2) %>%  # Keep only groups with exactly 2 occurrence of name_owner
  ungroup() %>%
  arrange(name_owner)

# This tells me that there are 4 facilities in Group 5.1 with 2 different id_operation_DOA
owner_doa_check <- occ_2_name_owner %>%
  group_by(name_owner) %>%
  filter(!is.na(id_operation_DOA)) %>%
  summarize(unique_doa_count = n_distinct(id_operation_DOA)) %>%
  ungroup() 

# This allowed me to check that there are NO facilities in occ_2_name_owner such that id_operation_DOA is NA
owners_all_na_doa <- occ_2_name_owner %>%
  group_by(name_owner) %>%
  filter(all(is.na(id_operation_DOA))) %>%  # Keep groups where all id_operation_DOA values are NA
  ungroup() 

# Remove the 4 facilities that have more than 1 id_operation_DOA
occ_2_name_owner_filtered <- occ_2_name_owner %>%
  filter(!name_owner %in% c("Burnett Farms", "Carroll Family Farms Partnership", "Chris and Michelle Apke", "Wayne A. Bergbower"))

# Count non-NA values for each row
occ_2_name_owner_select <- occ_2_name_owner_filtered %>%
  select(name_facility, name_owner, id_operation_DOA, county, animalTypes, address, lat_plss, lon_plss, lat_raw, lon_raw) %>%
 mutate(non_na_count = rowSums(!is.na(.)))  

# Group by name_owner and keep the row with the most non-NA values
occ_2_name_owner_final <- occ_2_name_owner_select %>%
  group_by(name_owner) %>%
  slice_max(order_by = non_na_count, n = 1, with_ties = FALSE) %>%  # Keep the row with the most non-NA values
  select(-non_na_count)  # Remove the helper column

# Checked that occ_2_name_owner_final contains (1) each unique name_owner from occ_2_name_owner_filtered, (2) the address and coords for the facilities for which this information is given, and (3) the id_operation_DOA for each row (which corresponds to 1 name_owner)
```

### Group 5.2: The 4 facilities excluded previously (for which the same name_owner occupies 2 rows, each corresponding to a different id_operation_DOA)

```{r}
Fac_4 <- anti_join(occ_2_name_owner, occ_2_name_owner_filtered) %>%
  select(name_facility, name_owner, id_operation_DOA, county, animalTypes, address, lat_plss, lon_plss, lat_raw, lon_raw)

# The following dataset is saved and reviewed in Excel. Relevant entries from here are included in doa_final_gp1_gp2_gp4_gp5 (latest combined doa dataset).
write.csv(Fac_4, file.path(file_path, "4 facilities.csv"), row.names = FALSE)
```

### Group 5.3: Those entries with no name_facility and same name_owner appears once or more than 2 times (i.e., facilities in DOA_no_name_facility but not in occ_2_name_owner)

```{r}
no_name_fac_rest <- anti_join(DOA_no_name_facility, occ_2_name_owner) %>%
  select(name_facility, name_owner, id_operation_DOA, county, animalTypes, address, lat_plss, lon_plss, lat_raw, lon_raw)

# Latest doa dataset with all of the above operations integrated
doa_latest <- read_csv(file.path(file_path, "doa_final_gp1_gp2_gp4_gp5.csv"))

# Entries in no_name_fac_rest for which id_operation_DOA is also present in doa_latest
no_name_fac_rest_1 <- no_name_fac_rest %>% 
  semi_join(doa_latest, by = "id_operation_DOA") %>%
  filter(!is.na(id_operation_DOA))

write.csv(no_name_fac_rest, file.path(file_path, "no_name_fac_rest.csv"), row.names = FALSE)

# Reviewed this dataset and added relevant entries to doa_final_gp1_gp2_gp4_gp5. Approach: matched facilities in no_name_fac_rest_1 with the latest doa dataset (i.e., those with id_operation_DOA present in both latest doa dataset and no_name_fac_rest); then matched facilities in no_name_fac_rest that have address and coords given with facilities in the latest doa dataset. Then deleted redundant rows and collapsed to faciliy-by-name-owner level.
```

### Including facilities in group 5.1 to latest doa dataset

```{r}
doa_latest_2 <- read_csv(file.path(file_path, "doa_final_gp1_gp2_gp4_gp5.csv"))

# Those in occ_2_name_owner_final where the id_operation_DOA is also present in doa_latest_2
gp_5_1_filtered <- occ_2_name_owner_final %>% 
  semi_join(doa_latest_2, by = "id_operation_DOA") 

# Add a flag column to mark rows that are in gp_5_1_filtered
occ_2_name_owner_final <- occ_2_name_owner_final %>%
  mutate(
    marked = if_else(id_operation_DOA %in% gp_5_1_filtered$id_operation_DOA, "Yes", "No")
  )
  
write.csv(occ_2_name_owner_final, file.path(file_path, "gp_5.1.csv"), row.names = FALSE)

# Reviewed this in Excel and added relevant entries to doa_final_gp1_gp2_gp4_gp5. Approach: matched facilities in gp_5_1_filtered with latest doa dataset (i.e., those with id_operation_DOA present in both latest doa dataset and occ_2_name_owner_final); then matched facilities in occ_2_name_owner_final that have address and coords given with the facilities in the latest doa dataset. Can't do much with the rest (that have no address/coords info and no matching id_operation_DOA so they are just included as individual facilities.

```

## Final DOA dataset

```{r}

doa_final_gp1_gp2_gp4_gp5 <- read_csv(file.path(file_path, "doa_final_gp1_gp2_gp4_gp5.csv"))

# Filter rows where either id_operation_DOA or my_Id_facility_doa is NA (final check)
na_entries <- doa_final_gp1_gp2_gp4_gp5 %>%
  filter(is.na(id_operation_DOA) | is.na(my_Id_facility_doa))

# Combine animalTypes for each unique my_Id_facility_doa
doa_final <- doa_final_gp1_gp2_gp4_gp5 %>%
  group_by(my_Id_facility_doa) %>%
  mutate(animalTypes = paste(unique(animalTypes), collapse = "; ")) %>%
  ungroup() # This is my final IL DOA dataset
write.csv(doa_final, file.path(file_path, "IL-DOA_final.csv"), row.names = FALSE)

# Rows in doa dataset for which coords are all NA but address is not
num_unique_missing_coords <- doa_final %>%
  filter(!is.na(address) & is.na(lat_plss) & is.na(lon_plss) & is.na(lat_raw) & is.na(lon_raw)) #436 rows (not unique facilities that have an address but not coords)


# Rows in doa dataset for which address and coords are all NA
num_unique_missing_loc <- doa_final %>%
  filter(is.na(address) & is.na(lat_plss) & is.na(lon_plss) & is.na(lat_raw) & is.na(lon_raw)) # 471 such rows


# Remove rows where all specified columns are NA (this dataset still has facilities which have an address, but NA for the coord columns)
doa_final_cleaned <- doa_final %>%
  filter(!(is.na(address) & is.na(lat_plss) & is.na(lon_plss) & is.na(lat_raw) & is.na(lon_raw))) %>% 
  filter(!grepl("\\b(RR|Box)\\b", address, ignore.case = TRUE)) #removed all rows where the address has RR or Box 

doa_final_cleaned <- doa_final_cleaned %>%
  mutate(
    # Create new lat_doa and lon_doa columns
    lat_doa = ifelse(!is.na(lat_plss), lat_plss, lat_raw),
    lon_doa = ifelse(!is.na(lon_plss), lon_plss, lon_raw)
  ) %>%
  # Remove the original lat_plss, lon_plss, lat_raw, lon_raw columns
  select(-lat_plss, -lon_plss, -lat_raw, -lon_raw)

# For each row, if lat_plss and lon_plss are not NA, those values are used for lat_doa and lon_doa. If lat_plss and lon_plss are NA, the corresponding lat_raw and lon_raw values are used instead.


# Number of unique facilities in doa vs epa dataset

raw_IL_EPA_2 <- read_csv("/Users/zarrinali/Documents/AFOs_IL/dataRAW_Zarrin/raw_IL-EPA-2.csv")
  
num_unique_facilities_doa <- doa_final_cleaned %>%
  summarise(unique_facilities = n_distinct(my_Id_facility_doa))
num_unique_facilities_epa <- raw_IL_EPA_2 %>%
  summarise(unique_facilities = n_distinct(myId_facility_epa)) # 1181 doa facilities vs 814 epa facilities

```

------------------------------------------------------------------------

# EPA-DOA matching

```{r}
file_path_2 <- "/Users/zarrinali/Documents/AFOs_IL/dataINTERM_Zarrin/DOA-EPA matching"

epa_final <- raw_IL_EPA_2 %>%
  select(name_facility, name_operator, myId_facility_epa, npdes, county, animalTypes, address, lat, lon) 
  
epa_final_cleaned <- epa_final %>%
  filter(!(is.na(address) & is.na(lat) & is.na(lon))) %>% 
  filter(!grepl("\\b(RR|Box)\\b", address, ignore.case = TRUE)) # removed all rows where address and coords were NA OR coords were NA, there was an address but the address contained the words RR or box


# Matching epa-doa dataset by name_facility
matches_raw_doa_epa <- fuzzyjoin::stringdist_join(
  x = doa_final_cleaned,
  y = epa_final_cleaned,
  by = "name_facility",
  method = 'cosine',
  max_dist = 10,
  mode = 'left', # left join includes all rows from doa_final and matched rows epa_final
  ignore_case = T,
  distance_col = "distance" # store the string distances
)

matches_raw_doa_epa <- matches_raw_doa_epa %>%
  select(name_facility.x, name_facility.y, distance, name_owner, name_operator, my_Id_facility_doa, myId_facility_epa, address.x, address.y, county.x, county.y, animalTypes.x, animalTypes.y, lat_doa, lon_doa, lat, lon, everything()) %>%
  rename(name_facility_doa = name_facility.x, name_facility_epa = name_facility.y, name_owner_doa = name_owner, name_operator_epa = name_operator, address_doa = address.x, address_epa = address.y, county_doa = county.x, county_epa = county.y, animalTypes_doa = animalTypes.x, animalTypes_epa = animalTypes.y, lat_epa = lat, lon_epa = lon)

# Filter: drop very bad matches and keep 5 best matches -> drop matches for which county doesn't match then keep 5 best matches
matches_filtered_doa_epa <- matches_raw_doa_epa %>%
  filter(county_doa==county_epa) %>% # Filter out matches that are not in the same county
  select(-county_epa) %>%
  rename(county = county_doa) %>%
  group_by(my_Id_facility_doa) %>% # Each facility is identified by the unique facility identifier I created before
  arrange(distance) %>%
  filter(row_number()<=5) # then keep the 5 best matches for each facility

# Simplifying dataset for determining threshold
matches_filtered_doa_epa_1 <- matches_filtered_doa_epa %>%
  filter(distance != 0) # Determine the threshold for high-quality matches using this dataset

# High quality matches
matched_doa_epa_good <- matches_filtered_doa_epa %>%
  filter(distance < 0.1) %>%
  group_by(my_Id_facility_doa) %>%
  filter(distance==min(distance)) %>% ungroup # For each doa facility (as identified by the unique identifier), keep the match with the smallest dist

# Remaining matches 
matched_doa_epa_not_good <- matches_filtered_doa_epa %>%
  anti_join(matched_doa_epa_good %>% select(my_Id_facility_doa), by = "my_Id_facility_doa") %>% # Excludes doa facilities already in the good matches dataset
  arrange(my_Id_facility_doa, distance) # Groups doa facilities together and arranges by distance

```

## Create 3 different groups of matches for separate treatment

```{r}
# Group 1: Matches for which name_facility_doa = name_facility_epa
matched_gp1_doa_epa <- matched_doa_epa_good %>% 
  filter(distance == 0) %>%
  mutate(state = "IL", lat_correct = NA, lon_correct = NA, address_correct = NA, comment = NA, id_new_likeNPDES = NA) %>%
  select(state, id_operation_DOA, my_Id_facility_doa, name_owner_doa, name_facility_doa, npdes, id_new_likeNPDES, myId_facility_epa, name_facility_epa, lat_doa, lon_doa, lat_epa, lon_epa, lat_correct, lon_correct, address_doa, address_epa, address_correct, animalTypes_doa, animalTypes_epa, comment) %>%
  arrange(my_Id_facility_doa, myId_facility_epa)

write.csv(matched_gp1_doa_epa, file.path(file_path_2, "gp_1_doa_epa.csv"), row.names = FALSE)

# Group 2: High quality matches for which name_facility_doa is NOT same as name_facility_epa (0 < dist < 0.1)
matched_gp2_doa_epa <- matched_doa_epa_good %>% 
  filter(distance != 0) %>% # Only the match with the minimum distance is kept for each name_facility_doa
  mutate(state = "IL", lat_correct = NA, lon_correct = NA, address_correct = NA, comment = NA, id_new_likeNPDES = NA) %>%
  select(state, id_operation_DOA, my_Id_facility_doa, name_owner_doa, name_facility_doa, npdes, id_new_likeNPDES, myId_facility_epa, name_operator_epa, name_facility_epa, lat_doa, lon_doa, lat_epa, lon_epa, lat_correct, lon_correct, address_doa, address_epa, address_correct, animalTypes_doa, animalTypes_epa, comment) %>%
  arrange(my_Id_facility_doa, myId_facility_epa)

write.csv(matched_gp2_doa_epa, file.path(file_path_2, "gp_2_doa_epa.csv"), row.names = FALSE)

# Group 3: Remaining matches (excludes doa facility Ids already in groups 1 and 2)
matched_gp3_doa_epa <-matched_doa_epa_not_good %>%
  mutate(state = "IL", lat_correct = NA, lon_correct = NA, address_correct = NA, comment = NA, id_new_likeNPDES = NA) %>%
  select(state, id_operation_DOA, my_Id_facility_doa, name_owner_doa, name_facility_doa, npdes, id_new_likeNPDES, myId_facility_epa, name_operator_epa, name_facility_epa, distance, lat_doa, lon_doa, lat_epa, lon_epa, lat_correct, lon_correct, address_doa, address_epa, address_correct, animalTypes_doa, animalTypes_epa, comment) %>%
  arrange(my_Id_facility_doa, distance) # For each doa facility, the best 5 matches are kept and arranged by distance

write.csv(matched_gp3_doa_epa, file.path(file_path_2, "gp_3_doa_epa.csv"), row.names = FALSE)


```

## Group 1: Matches for which facility name matches exactly

```{r}
# Checking coords to see if the matches for epa and doa facilities are within a reasonable distance 

# Load required package
library(geosphere)

matched_gp1_doa_epa <- matched_gp1_doa_epa %>%
  mutate(
    distance = ifelse(
      is.na(lat_doa) | is.na(lon_doa) | is.na(lat_epa) | is.na(lon_epa), 
      NA, 
      distHaversine(cbind(lon_doa, lat_doa), cbind(lon_epa, lat_epa))
    )
  ) %>%
  select(my_Id_facility_doa, name_facility_doa, name_facility_epa, address_doa, address_epa, distance, everything())


# Dataset where distance is less than 2100 meters (these are matches across the 2 datasets)
matched_distance_less_2100 <- matched_gp1_doa_epa %>%
  filter(!is.na(distance) & distance < 2100) %>%
  select(address_doa, address_epa, distance, lat_doa, lon_doa, lat_epa, lon_epa, everything()) #to be added to final dataset

# Dataset where distance is greater than 2100 meters (these are not matches)
matched_distance_greater_2100 <- matched_gp1_doa_epa %>%
  filter(!is.na(distance) & distance > 2100)

# Dataset where distance is NA (have to manually check these in Excel)
matched_distance_na <- matched_gp1_doa_epa %>%
  filter(is.na(distance))
write.csv(matched_distance_na, file.path(file_path_2, "matched_distance_na.csv"), row.names = FALSE) #Export to Excel

# Coords distance is NA but manually checked in Excel (using given address/coords) that these are matches

yes_matches_distance_na <- read_csv(file.path(file_path_2, "yes_matches_distance_na.csv")) #to be added to final dataset

# Coords distance is NA and checked manually that these are NOT matches
no_matches_dist_na <- read_csv(file.path(file_path_2, "no_matches_dist_na.csv"))

# Merge the two datasets that do not have matches
merged_no_matches <- bind_rows(no_matches_dist_na, matched_distance_greater_2100) #each of these facilities (doa and epa) have to be separately added to the final dataset
  
```

### Prep the final datasets in Group 1

```{r}
# matched_distance_less_2100


# Find cases where the same my_Id_facility_doa is matched to multiple myId_facility_epa
doa_to_multiple_epa <- matched_distance_less_2100 %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(myId_facility_epa) > 1) %>%
  ungroup()

# Find cases where the same myId_facility_epa is matched to multiple my_Id_facility_doa
epa_to_multiple_doa <- matched_distance_less_2100 %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup()

# Combine the results to see all problematic rows
problematic_rows <- bind_rows(doa_to_multiple_epa, epa_to_multiple_doa) %>%
  distinct()
write.csv(problematic_rows, file.path(file_path_2, "problematic_rows.csv"), row.names = FALSE)

#In Excel I deleted the rows that were not matches so that now every unique my_Id_facility_doa is mapped to one unique myId_facility_epa
problematic_rows_solved <- read_csv(file.path(file_path_2, "problematic_rows_solved.csv"))


matched_dist_less_2100_combined <- matched_distance_less_2100 %>%
  anti_join(problematic_rows) %>% 
  bind_rows(problematic_rows_solved)


# Cleaning up the data

matched_dist_less_2100_final <- matched_dist_less_2100_combined %>%
  mutate(
    # Fill address_correct with the longest entry between address_doa and address_epa, considering NA values
    address_correct = case_when(
      is.na(address_doa) ~ address_epa,  # Use address_epa if address_doa is NA
      is.na(address_epa) ~ address_doa,  # Use address_doa if address_epa is NA
      nchar(address_epa) > nchar(address_doa) ~ address_epa,  # Use address_epa if it's longer
      TRUE ~ address_doa  # Otherwise, use address_doa
    ),
    # Fill lat_correct with lat_epa if available, otherwise lat_doa
    lat_correct = ifelse(!is.na(lat_epa), lat_epa, lat_doa),
    # Fill lon_correct with lon_epa if available, otherwise lon_doa
    lon_correct = ifelse(!is.na(lon_epa), lon_epa, lon_doa)
  ) %>%
   select(state, name_facility_epa, myId_facility_epa, id_operation_DOA, name_owner_doa, name_facility_doa, my_Id_facility_doa, lat_correct, lon_correct, address_correct) # THIS DATASET IS COMPLETE

```

```{r}
# yes_matches_distance_na


# Find cases where the same my_Id_facility_doa is matched to multiple myId_facility_epa
doa_to_multiple_epa_1 <- yes_matches_distance_na %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(myId_facility_epa) > 1) %>%
  ungroup() # NO ENTRIES

# Find cases where the same myId_facility_epa is matched to multiple my_Id_facility_doa
epa_to_multiple_doa_1 <- yes_matches_distance_na %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() #NO ENTRIES




# Cleaning up the data

yes_matches_distance_na_final <- yes_matches_distance_na %>%
  mutate(
    # Fill address_correct with the longest entry between address_doa and address_epa, considering NA values
    address_correct = case_when(
      is.na(address_doa) ~ address_epa,  # Use address_epa if address_doa is NA
      is.na(address_epa) ~ address_doa,  # Use address_doa if address_epa is NA
      nchar(address_epa) > nchar(address_doa) ~ address_epa,  # Use address_epa if it's longer
      TRUE ~ address_doa  # Otherwise, use address_doa
    ),
    # Fill lat_correct with lat_epa if available, otherwise lat_doa
    lat_correct = ifelse(!is.na(lat_epa), lat_epa, lat_doa),
    # Fill lon_correct with lon_epa if available, otherwise lon_doa
    lon_correct = ifelse(!is.na(lon_epa), lon_epa, lon_doa)
  ) %>%
   select(state, name_facility_epa, myId_facility_epa, id_operation_DOA, name_owner_doa, name_facility_doa, my_Id_facility_doa, lat_correct, lon_correct, address_correct) # THIS DATASET IS COMPLETE

```

------------------------------------------------------------------------

## Group 2: Matches for which facility name string dist is between 0 and 0.1

```{r}
# Checking coords to see if the matches for epa and doa facilities are within a reasonable distance 

# Load required package
library(geosphere)

# Suppress scientific notation
options(scipen = 999)

# Compute coords distances and update the dataset
matched_gp2_doa_epa <- matched_gp2_doa_epa %>%
  mutate(
    distance = ifelse(
      is.na(lat_doa) | is.na(lon_doa) | is.na(lat_epa) | is.na(lon_epa), 
      NA, 
      distHaversine(cbind(lon_doa, lat_doa), cbind(lon_epa, lat_epa))
    )
  ) %>%
  select(my_Id_facility_doa, name_facility_doa, name_facility_epa, address_doa, address_epa, distance, everything())


# Dataset where distance is less than 1000 meters (these are matches across the 2 datasets)
matched_distance_less_1000 <- matched_gp2_doa_epa %>%
  filter(!is.na(distance) & distance < 1000) %>%
  select(address_doa, address_epa, distance, lat_doa, lon_doa, lat_epa, lon_epa, everything()) #to be added to final dataset

# Dataset where distance is greater than 1000 meters (these are not matches)
matched_distance_greater_1000 <- matched_gp2_doa_epa %>%
  filter(!is.na(distance) & distance > 1000)

# Dataset where distance is NA (have to manually check these in Excel)
matched_distance_na_gp2 <- matched_gp2_doa_epa %>%
  filter(is.na(distance))
write.csv(matched_distance_na_gp2, file.path(file_path_2, "matched_distance_na_gp2.csv"), row.names = FALSE) # manually check in Excel if these are matches since dist b/w epa and doa coords is NA



# Coords distance is NA but manually checked in Excel (using given address/coords) that these are matches
yes_matches_dist_na_gp2 <- read_csv(file.path(file_path_2, "yes_matches_dist_na_gp2.csv")) #to be added to final dataset

# Coords distance is NA and checked manually that these are NOT matches
no_matches_dist_na_gp2 <- read_csv(file.path(file_path_2, "no_matches_dist_na_gp2.csv"))

# Merge the two datasets that do not have matches
merged_no_matches_2 <- bind_rows(no_matches_dist_na_gp2, matched_distance_greater_1000) #each of these facilities (doa and epa) have to be separately added to the final dataset

```

### Prep the final datasets in Group 2

```{r}
# matched_distance_less_1000


# Find cases where the same my_Id_facility_doa is matched to multiple myId_facility_epa
doa_to_multiple_epa_2 <- matched_distance_less_1000 %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(myId_facility_epa) > 1) %>%
  ungroup() #NO ENTRIES

# Find cases where the same myId_facility_epa is matched to multiple my_Id_facility_doa
epa_to_multiple_doa_2 <- matched_distance_less_1000 %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() # 2 entries here. This is a mistake on my part because the same doa facility is given two different my_Id_facility_doa.

#Fixing the above mistake
matched_distance_less_1000 <- matched_distance_less_1000 %>% mutate(my_Id_facility_doa = ifelse(id_operation_DOA == "LF143013", "ildoa_1394", my_Id_facility_doa))

# Fixing the myId_facility_doa in doa_final_cleaned which will be the dataset used to identify facilities that have no matches
doa_final_cleaned <- doa_final_cleaned %>% mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "ildoa_1395", "ildoa_1394", my_Id_facility_doa))



# Cleaning up the data
matched_distance_less_1000_final <- matched_distance_less_1000 %>%
  mutate(
    # Fill address_correct with the longest entry between address_doa and address_epa, considering NA values
    address_correct = case_when(
      is.na(address_doa) ~ address_epa,  # Use address_epa if address_doa is NA
      is.na(address_epa) ~ address_doa,  # Use address_doa if address_epa is NA
      nchar(address_epa) > nchar(address_doa) ~ address_epa,  # Use address_epa if it's longer
      TRUE ~ address_doa  # Otherwise, use address_doa
    ),
    # Fill lat_correct with lat_epa if available, otherwise lat_doa
    lat_correct = ifelse(!is.na(lat_epa), lat_epa, lat_doa),
    # Fill lon_correct with lon_epa if available, otherwise lon_doa
    lon_correct = ifelse(!is.na(lon_epa), lon_epa, lon_doa)
  ) %>%
   select(state, name_facility_epa, myId_facility_epa, id_operation_DOA, name_owner_doa, name_facility_doa, my_Id_facility_doa, lat_correct, lon_correct, address_correct) # THIS DATASET IS COMPLETE

```

```{r}
# yes_matches_dist_na_gp2

# Find cases where the same my_Id_facility_doa is matched to multiple myId_facility_epa
doa_to_multiple_epa_3 <- yes_matches_dist_na_gp2 %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(myId_facility_epa) > 1) %>%
  ungroup() #NO ENTRIES

# Find cases where the same myId_facility_epa is matched to multiple my_Id_facility_doa
epa_to_multiple_doa_3 <- yes_matches_dist_na_gp2 %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() #NO ENTRIES


# Cleaning up the data
yes_matches_dist_na_gp2_final <- yes_matches_dist_na_gp2 %>%
  mutate(
    # Fill address_correct with the longest entry between address_doa and address_epa, considering NA values
    address_correct = case_when(
      is.na(address_doa) ~ address_epa,  # Use address_epa if address_doa is NA
      is.na(address_epa) ~ address_doa,  # Use address_doa if address_epa is NA
      nchar(address_epa) > nchar(address_doa) ~ address_epa,  # Use address_epa if it's longer
      TRUE ~ address_doa  # Otherwise, use address_doa
    ),
    # Fill lat_correct with lat_epa if available, otherwise lat_doa
    lat_correct = ifelse(!is.na(lat_epa), lat_epa, lat_doa),
    # Fill lon_correct with lon_epa if available, otherwise lon_doa
    lon_correct = ifelse(!is.na(lon_epa), lon_epa, lon_doa)
  ) %>%
   select(state, name_facility_epa, myId_facility_epa, id_operation_DOA, name_owner_doa, name_facility_doa, my_Id_facility_doa, lat_correct, lon_correct, address_correct) # THIS DATASET IS COMPLETE

```

------------------------------------------------------------------------

## Group 3: Low quality matches of facility names

```{r}
# Load the stringdist package
library(stringdist)


# Checking coords to see if the matches for epa and doa facilities are within a reasonable distance 
matched_gp3_doa_epa <- matched_gp3_doa_epa %>%
  mutate(
    coordsdist = ifelse(
      is.na(lat_doa) | is.na(lon_doa) | is.na(lat_epa) | is.na(lon_epa), 
      NA, 
      distHaversine(cbind(lon_doa, lat_doa), cbind(lon_epa, lat_epa))
    )
  ) %>%
  select(my_Id_facility_doa, name_facility_doa, name_facility_epa, address_doa, address_epa, distance, coordsdist, everything())


# Dataset where coords distance is NA (have to manually check these in Excel)
matched_distance_na_gp3 <- matched_gp3_doa_epa %>%
  filter(is.na(coordsdist)) #956 entries

# Impossible to go through 956 entries to find matches, so find the string distance between the address_doa and address_epa and if it is below a certain threshold then check if it is a match
# Add a new column with the cosine string distance between address_doa and address_epa
matched_distance_na_gp3 <- matched_distance_na_gp3 %>%
  mutate(
    addressdist = stringdist(address_doa, address_epa, method = "cosine")
  ) %>%
  select(name_facility_doa, name_facility_epa, address_doa, address_epa, addressdist, distance, coordsdist, everything())

# Filter rows where addressdist < 0.13 or addressdist is NA (these could be matches, so check in Excel)
matched_dist_na_gp3_1 <- matched_distance_na_gp3 %>%
  filter(is.na(addressdist) | addressdist < 0.13) # manually check this dataset
write.csv(matched_dist_na_gp3_1, file.path(file_path_2, "matched_dist_na_gp3_1.csv"), row.names = FALSE) #check in Excel

# From Excel (I very carefully made sure to evaluate matches for which addressdist < 0.13 but for the ones where addressdist is NA, I only checked a few (b/c it seemed extremely unlikely that there were any matches))
good_dist_na_gp3 <- read_csv(file.path(file_path_2,"good_dist_na_gp3.csv")) # matches
bad_dist_na_gp3 <- read_csv(file.path(file_path_2, "bad_dist_na_gp3.csv")) # no matches


# NO MATCHES
no_matches_dist_na_gp3 <- bind_rows(matched_distance_na_gp3 %>% filter(addressdist > 0.13), bad_dist_na_gp3)



#Dataset where coords dist < 2000 (these could be potential matches but I will check further in Excel)
matched_dist_less_2000 <- matched_gp3_doa_epa %>%
  filter(!is.na(coordsdist) & coordsdist < 2000) %>%
  select(address_doa, address_epa, coordsdist, lat_doa, lon_doa, lat_epa, lon_epa, everything()) #manually check in Excel
write.csv(matched_dist_less_2000, file.path(file_path_2, "matched_dist_less_2000.csv"), row.names = FALSE)

# From Excel
yes_matches_dist_less_2000 <- read_csv(file.path(file_path_2, "yes_matches_dist_less_2000.csv")) # matches

no_matches_dist_less_2000 <- read_csv(file.path(file_path_2, "no_matches_dist_less_2000.csv")) #NO MATCHES

# NO MATCHES 
dist_greater_2000 <- matched_gp3_doa_epa %>%
  filter(coordsdist > 2000)

# Merge the 3 datasets in Group 3 that do not have any matches
merged_no_matches_3 <- bind_rows(no_matches_dist_na_gp3, no_matches_dist_less_2000, dist_greater_2000) #each of these facilities (doa and epa) have to be separately added to the final dataset
```

### Prep the final datasets in Group 3

```{r}
# good_dist_na_gp3

# Find cases where the same my_Id_facility_doa is matched to multiple myId_facility_epa
doa_to_multiple_epa_4 <- good_dist_na_gp3 %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(myId_facility_epa) > 1) %>%
  ungroup() # No entries

# Find cases where the same myId_facility_epa is matched to multiple my_Id_facility_doa
epa_to_multiple_doa_4 <- good_dist_na_gp3 %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() # 5 entries. This is a mistake on my part because the same doa facility is given 3 different my_Id_facility_doa.

# Fixing the above mistake
good_dist_na_gp3 <- good_dist_na_gp3 %>% mutate(my_Id_facility_doa = ifelse(address_doa == "23318 W Taggert Rd, Elmwood, IL 61529", "ildoa_319", my_Id_facility_doa))

# Fixing the myId_facility_doa in doa_final_cleaned which will be the dataset used to identify facilities that have no matches
doa_final_cleaned <- doa_final_cleaned %>% mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "ildoa_491", "ildoa_319", my_Id_facility_doa)) %>%
  mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "ildoa_760", "ildoa_319", my_Id_facility_doa))


# Cleaning up the data
good_dist_na_gp3_final <- good_dist_na_gp3 %>%
  mutate(
    # Fill address_correct with the longest entry between address_doa and address_epa, considering NA values
    address_correct = case_when(
      is.na(address_doa) ~ address_epa,  # Use address_epa if address_doa is NA
      is.na(address_epa) ~ address_doa,  # Use address_doa if address_epa is NA
      nchar(address_epa) > nchar(address_doa) ~ address_epa,  # Use address_epa if it's longer
      TRUE ~ address_doa  # Otherwise, use address_doa
    ),
    # Fill lat_correct with lat_epa if available, otherwise lat_doa
    lat_correct = ifelse(!is.na(lat_epa), lat_epa, lat_doa),
    # Fill lon_correct with lon_epa if available, otherwise lon_doa
    lon_correct = ifelse(!is.na(lon_epa), lon_epa, lon_doa)
  ) %>%
   select(state, name_facility_epa, myId_facility_epa, id_operation_DOA, name_owner_doa, name_facility_doa, my_Id_facility_doa, lat_correct, lon_correct, address_correct) # THIS DATASET IS COMPLETE

```

```{r}
# yes_matches_dist_less_2000

# Find cases where the same my_Id_facility_doa is matched to multiple myId_facility_epa
doa_to_multiple_epa_5 <- yes_matches_dist_less_2000 %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(myId_facility_epa) > 1) %>%
  ungroup() # 2 entries

# Fixing the problem because the two different myId_facility_epa are referring to the same facility
yes_matches_dist_less_2000 <- yes_matches_dist_less_2000 %>% mutate(myId_facility_epa = ifelse(my_Id_facility_doa == "ildoa_513", "ilepa_578", myId_facility_epa))

# Fixing the myId_facility_epa in epa_final_cleaned which will be one of the two datasets used to identify facilities that have no matches
epa_final_cleaned <- epa_final_cleaned %>% mutate(myId_facility_epa = ifelse(myId_facility_epa == "ilepa_727", "ilepa_578", myId_facility_epa))


# Find cases where the same myId_facility_epa is matched to multiple my_Id_facility_doa
epa_to_multiple_doa_5 <- yes_matches_dist_less_2000 %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() # 11 entries

# Fixing the problem b/c two different my_Id_facility_doa are referring to the same facility
yes_matches_dist_less_2000 <- yes_matches_dist_less_2000 %>% mutate(my_Id_facility_doa = ifelse(myId_facility_epa == "ilepa_152", "ildoa_961", my_Id_facility_doa)) %>%
  mutate(my_Id_facility_doa = ifelse(myId_facility_epa == "ilepa_571", "ildoa_761", my_Id_facility_doa))

# Fixing the myId_facility_doa in doa_final_cleaned which will be the dataset used to identify facilities that have no matches
doa_final_cleaned <- doa_final_cleaned %>% mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "ildoa_1004", "ildoa_961", my_Id_facility_doa)) %>%
  mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "ildoa_1415", "ildoa_761", my_Id_facility_doa))


# Cleaning up the data
yes_matches_dist_less_2000_final <- yes_matches_dist_less_2000 %>%
  mutate(
    # Fill address_correct with the longest entry between address_doa and address_epa, considering NA values
    address_correct = case_when(
      is.na(address_doa) ~ address_epa,  # Use address_epa if address_doa is NA
      is.na(address_epa) ~ address_doa,  # Use address_doa if address_epa is NA
      nchar(address_epa) > nchar(address_doa) ~ address_epa,  # Use address_epa if it's longer
      TRUE ~ address_doa  # Otherwise, use address_doa
    ),
    # Fill lat_correct with lat_epa if available, otherwise lat_doa
    lat_correct = ifelse(!is.na(lat_epa), lat_epa, lat_doa),
    # Fill lon_correct with lon_epa if available, otherwise lon_doa
    lon_correct = ifelse(!is.na(lon_epa), lon_epa, lon_doa)
  ) %>%
   select(state, name_facility_epa, myId_facility_epa, id_operation_DOA, name_owner_doa, name_facility_doa, my_Id_facility_doa, lat_correct, lon_correct, address_correct) # THIS DATASET IS COMPLETE

```

------------------------------------------------------------------------

# Creating the epa-doa dataset

```{r}
carroll <- read_csv(file.path(file_path_2, "CarrollFarms_match_doa-epa.csv")) # matched by Claire


matches_carrollfarms <- read_csv(file.path(file_path_2, "new_CarrollFarms_match_doa-epa.csv")) #clean version

matches <- bind_rows(matched_dist_less_2100_final, yes_matches_distance_na_final, matched_distance_less_1000_final, yes_matches_dist_na_gp2_final, good_dist_na_gp3_final, yes_matches_dist_less_2000_final)

common_rows <- matches_carrollfarms %>%
  semi_join(matches, by = "id_operation_DOA") # 2 common rows between carroll farms and matches dataset

# Remove rows from matches that match id_operation_DOA in matches_carrollfarms
matches_1 <- matches %>%
  anti_join(matches_carrollfarms, by = "id_operation_DOA")


matches_2 <- bind_rows(matches_1, matches_carrollfarms)



# Find cases where the same my_Id_facility_doa is matched to multiple myId_facility_epa
doa_to_multiple_epa_6 <- matches_2 %>%
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(myId_facility_epa) > 1) %>%
  ungroup() #No entries

# Find cases where the same myId_facility_epa is matched to multiple my_Id_facility_doa
epa_to_multiple_doa_6 <- matches_2 %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() # 39 entries

# Fixing the issue in Excel
write.csv(matches_2, file.path(file_path_2, "matches_2.csv"), row.names = FALSE)
write.csv(doa_final_cleaned, file.path(file_path_2, "doa_final_cleaned.csv"), row.names = FALSE) # I deleted a couple of rows which werent actually matches and for the others there was a mistake (for instance, the same facility was given two different facility IDs) - fixed the IDs both in matches_2 and doa_final_cleaned

# From Excel
matches_3 <- read_csv(file.path(file_path_2, "matches_2_sorted.csv"))
doa_final_cleaned_1 <- read_csv(file.path(file_path_2, "doa_final_cleaned_sorted.csv"))

epa_to_multiple_doa_6_1 <- matches_3 %>%
  group_by(myId_facility_epa) %>%
  filter(n_distinct(my_Id_facility_doa) > 1) %>%
  ungroup() # NO ENTRIES - just checked to see if all the problem rows had been fixed



# Get rows from doa_final_cleaned_1 where my_Id_facility_doa is not in matches_3
doa_not_in_matches <- doa_final_cleaned_1 %>%
  anti_join(matches_3, by = "my_Id_facility_doa")

# Remove rows from doa_not_in_matches based on the following conditions
doa_not_in_matches_cleaned <- doa_not_in_matches %>%
  filter(is.na(id_operation_DOA) | ( # Leave rows with NA as they are
      !id_operation_DOA %in% carroll$id_operation_DOA & # Exclude rows matching carroll farms
      !id_operation_DOA %in% c("LF067035", "LF067046")  # Exclude rows with these two IDs which also correspond to carroll farms
    )
  )

# Get rows from epa_final_cleaned where myId_facility_epa is not in matches_3
epa_not_in_matches <- epa_final_cleaned %>%
  anti_join(matches_3, by = "myId_facility_epa")

# Remove rows with npdes in carroll
epa_not_in_matches_cleaned <- epa_not_in_matches %>%
  filter(
    is.na(npdes) | # Leave rows with NA as they are
      (!npdes %in% carroll$npdes) # Exclude rows with npdes in carroll farms
  )


doa_not_in_matches_final <- doa_not_in_matches_cleaned %>%
  select(-county, -animalTypes, # Remove unwanted columns
    name_facility_doa = name_facility,
    name_owner_doa = name_owner,
    address_correct = address, 
    lat_correct = lat_doa, 
    lon_correct = lon_doa
  ) %>%
  mutate(
    state = "IL", name_facility_epa = NA, myId_facility_epa = NA)



epa_not_in_matches_final <- epa_not_in_matches_cleaned %>%
  select(
    -name_operator, -npdes, -county, -animalTypes, # Remove unwanted columns
    name_facility_epa = name_facility,            # Rename columns
    address_correct = address, 
    lat_correct = lat, 
    lon_correct = lon
  ) %>%
  mutate(
    state = "IL", id_operation_DOA = NA, name_owner_doa = NA, name_facility_doa = NA, my_Id_facility_doa = NA)

# combined dataset of all the epa-doa matches + doa and epa facilities that do not have matches
epa_doa <- rbind(matches_3, doa_not_in_matches_final, epa_not_in_matches_final)

  
```

```{r}
# Cleaning up the coords of the epa-doa dataset

help_1 <- epa_doa %>%
  filter(!is.na(myId_facility_epa)) %>% # Exclude NA values for myId_facility_epa
  group_by(myId_facility_epa) %>%
  filter(n_distinct(lon_correct) > 1) # 56 entries

# Export epa_doa in Excel to keep the best set of coords
write.csv(epa_doa, file.path(file_path_2, "epa_doa.csv"), row.names = FALSE) 
# for a lot of the rows in help_1, there was a mistake in the id for the epa dataset where the same id was used for two diff facilities with 2 diff coords (fixed in Excel)

#From Excel
epa_doa_1 <- read_csv(file.path(file_path_2, "epa_doa_1.csv"))

help_2 <- epa_doa_1 %>%
  filter(!is.na(my_Id_facility_doa)) %>% # Exclude NA values for myId_facility_epa
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(lon_correct) > 1) # 18 entries - Export to Excel and fix manually

#From Excel 
epa_doa_2 <- read_csv(file.path(file_path_2, "epa_doa_2.csv"))


help_3 <- epa_doa_2 %>%
  filter(!is.na(my_Id_facility_doa)) %>% # Exclude NA values for myId_facility_epa
  group_by(my_Id_facility_doa) %>%
  filter(n_distinct(lon_correct) > 1) # now has 3 entries but their coords appear exactly the same (perhaps the diff is in a higher decimal place which doesn't really make a diff)

# The dataset epa_doa_2 is collapsed to the facility-by-name-by-name-owner level, that is, the same facility (identifid by my_Id_facility) corresponds to multiple rows if the name_owner or name_facility are event slightly different. We want to collapse the final dataset to 1 row per facility.

```

# Collapsing the dataset so that 1 row corresponds to 1 facility

```{r}
# Collapsing the name_owner_doa of facilities
library(stringdist)
epa_doa_3 <- epa_doa_2 %>%
  mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "", NA, my_Id_facility_doa)) %>%
  group_by(my_Id_facility_doa) %>%
  mutate(
    name_owner_doa = ifelse(
      is.na(my_Id_facility_doa), 
      name_owner_doa, # Leave rows with NA in my_Id_facility_doa as they are
      {
        # Get unique names in the group
        unique_names <- unique(name_owner_doa[!is.na(name_owner_doa)])
        
        if (length(unique_names) <= 1) {
          unique_names # If there's only one unique name, keep it
        } else {
          # Compute the pairwise string distance. If the string dist < 0.1 then we will keep the name that is longer. Otherwise we will keep both names separated by a semicolon.
          dist_matrix <- stringdistmatrix(unique_names, unique_names, method = "cosine")
          rownames(dist_matrix) <- unique_names
          colnames(dist_matrix) <- unique_names
          
          # Find and merge names with distance < 0.1
          merged_names <- character()
          while (length(unique_names) > 0) {
            current <- unique_names[1]
            close_matches <- unique_names[stringdist(current, unique_names, method = "cosine") < 0.1]
            longest_name <- close_matches[which.max(nchar(close_matches))]
            merged_names <- c(merged_names, longest_name)
            unique_names <- setdiff(unique_names, close_matches)
          }
          
          # Return merged names separated by a semicolon
          paste(unique(merged_names), collapse = "; ")
        }
      }
    )
  ) %>%
  ungroup()



```

```{r}
# Collapsing the name_facility_doa of facilities.

epa_doa_4 <- epa_doa_3 %>%
  mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "", NA, my_Id_facility_doa)) %>%
  group_by(my_Id_facility_doa) %>%
  mutate(
    name_facility_doa = ifelse(
      is.na(my_Id_facility_doa), 
      name_facility_doa, # Leave rows with NA in my_Id_facility_doa as they are
      {
        # Get unique names in the group
        unique_names <- unique(name_facility_doa[!is.na(name_facility_doa)])
        
        if (length(unique_names) <= 1) {
          unique_names # If there's only one unique name, keep it. If the string dist < 0.1 then we will keep the name that is longer. Otherwise we will keep both names separated by a semicolon.
        } else {
          # Compute the pairwise string distance
          dist_matrix <- stringdistmatrix(unique_names, unique_names, method = "cosine")
          rownames(dist_matrix) <- unique_names
          colnames(dist_matrix) <- unique_names
          
          # Find and merge names with distance < 0.1
          merged_names <- character()
          while (length(unique_names) > 0) {
            current <- unique_names[1]
            close_matches <- unique_names[stringdist(current, unique_names, method = "cosine") < 0.1]
            longest_name <- close_matches[which.max(nchar(close_matches))]
            merged_names <- c(merged_names, longest_name)
            unique_names <- setdiff(unique_names, close_matches)
          }
          
          # Return merged names separated by a semicolon
          paste(unique(merged_names), collapse = ";")
        }
      }
    )
  ) %>%
  ungroup()

```

```{r}
# Collapsing the name_facility_epa of facilities

epa_doa_5 <- epa_doa_4 %>%
  mutate(my_Id_facility_doa = ifelse(my_Id_facility_doa == "", NA, my_Id_facility_doa)) %>%
  group_by(my_Id_facility_doa) %>%
  mutate(
    name_facility_epa = ifelse(
      is.na(my_Id_facility_doa), 
      name_facility_epa, # Leave rows with NA in my_Id_facility_doa as they are
      {
        # Get unique names in the group
        unique_names <- unique(name_facility_epa[!is.na(name_facility_epa)])
        
        if (length(unique_names) <= 1) {
          unique_names # If there's only one unique name, keep it. If the string dist < 0.1 then we will keep the name that is longer. Otherwise we will keep both names separated by a semicolon.
        } else {
          # Compute the pairwise string distance
          dist_matrix <- stringdistmatrix(unique_names, unique_names, method = "cosine")
          rownames(dist_matrix) <- unique_names
          colnames(dist_matrix) <- unique_names
          
          # Find and merge names with distance < 0.1
          merged_names <- character()
          while (length(unique_names) > 0) {
            current <- unique_names[1]
            close_matches <- unique_names[stringdist(current, unique_names, method = "cosine") < 0.1]
            longest_name <- close_matches[which.max(nchar(close_matches))]
            merged_names <- c(merged_names, longest_name)
            unique_names <- setdiff(unique_names, close_matches)
          }
          
          # Return merged names separated by a semicolon
          paste(unique(merged_names), collapse = ";")
        }
      }
    )
  ) %>%
  ungroup()


# Now for my_Id_facility_epa which do not have a corresponding myId_facility_doa
epa_doa_6 <- epa_doa_5 %>%
  group_by(myId_facility_epa) %>%
  mutate(
    name_facility_epa = ifelse(
      !is.na(my_Id_facility_doa), 
      name_facility_epa, # Skip rows with a corresponding my_Id_facility_doa
      {
        # Get unique names in the group
        unique_names <- unique(name_facility_epa[!is.na(name_facility_epa)])
        
        if (length(unique_names) <= 1) {
          unique_names # If there's only one unique name, keep it. If the string dist < 0.1 then we will keep the name that is longer. Otherwise we will keep both names separated by a semicolon.
        } else {
          # Compute the pairwise string distance
          dist_matrix <- stringdistmatrix(unique_names, unique_names, method = "cosine")
          rownames(dist_matrix) <- unique_names
          colnames(dist_matrix) <- unique_names
          
          # Find and merge names with distance < 0.1
          merged_names <- character()
          while (length(unique_names) > 0) {
            current <- unique_names[1]
            close_matches <- unique_names[stringdist(current, unique_names, method = "cosine") < 0.1]
            longest_name <- close_matches[which.max(nchar(close_matches))]
            merged_names <- c(merged_names, longest_name)
            unique_names <- setdiff(unique_names, close_matches)
          }
          
          # Return merged names separated by a semicolon
          paste(unique(merged_names), collapse = "; ")
        }
      }
    )
  ) %>%
  ungroup()

```

```{r}
# Collapsing the id_operation_DOA of facilities to 1 row

epa_doa_7 <- epa_doa_6 %>%
  group_by(my_Id_facility_doa) %>%
  mutate(
    id_operation_DOA = ifelse(
      is.na(my_Id_facility_doa), 
      id_operation_DOA, # Leave rows with NA in my_Id_facility_doa as they are
      {
        # Get unique id_operation_DOA in the group
        unique_operations <- unique(id_operation_DOA[!is.na(id_operation_DOA)])
        
        if (length(unique_operations) == 0) {
          id_operation_DOA # If all rows have NA for id_operation_DOA, leave as is
        } else {
          # If there's more than one id_operation_DOA, join them with a semicolon
          paste(unique_operations, collapse = "; ")
        }
      }
    )
  ) %>%
  ungroup()


```

```{r}
# Making sure that each my_Id_facility_doa and each myId_facility_epa corresponds to just one address and set of coords

epa_doa_8 <- epa_doa_7 %>%
  group_by(my_Id_facility_doa) %>%
  mutate(
    # If my_Id_facility_doa is NA, keep the original values
    address_correct = ifelse(is.na(my_Id_facility_doa), address_correct, address_correct[which.max(nchar(address_correct))]),
    lat_correct = ifelse(is.na(my_Id_facility_doa), lat_correct, first(lat_correct)),
    lon_correct = ifelse(is.na(my_Id_facility_doa), lon_correct, first(lon_correct)) # Recall that the coords were checked previously to retain the most accurate one for each facility and this was applied to all rows corresponding that facility.
  ) %>%
  ungroup() # Ungroup to ensure all rows are kept

epa_doa_9 <- epa_doa_8 %>%
  group_by(myId_facility_epa) %>%
  mutate(
    # If myId_facility_epa is NA, keep the original values
    address_correct = ifelse(is.na(myId_facility_epa), address_correct, address_correct[which.max(nchar(address_correct))]),
    lat_correct = ifelse(is.na(my_Id_facility_doa), lat_correct, first(lat_correct)),
    lon_correct = ifelse(is.na(my_Id_facility_doa), lon_correct, first(lon_correct)) # Recall that the coords were checked previously to retain the most accurate one for each facility and this was applied to all rows corresponding that facility.
  ) %>%
  ungroup() # Ungroup to ensure all rows are kept


epa_doa_final <- epa_doa_9 %>%
  distinct() # Checked that each row corresponds to a unique my_Id_facility_doa and myId_facility_epa and that the same ID does not appear in more than 1 row.

write.csv(epa_doa_final, file.path(file_path_2, "epa_doa_final.csv"), row.names = FALSE)


matches_DOA_EPA <- read_excel(file.path(file_path_2, "matches_DOA-EPA-2.xlsx")) # Some of the facilities here are repeated in epa_doa_final so I will manually go through them in Excel and combine the two datasets


# From Excel. Final dataset: this is the dataset that contains facilities from both epa_doa_final and matches_DOA_EPA
matches_epa_doa_final <- read_csv("/Users/zarrinali/Documents/AFOs_IL/dataFINAL_Zarrin/matches_epa_doa_final.csv")

```
