---
title: "Consumption Regressions"
output:
  html_document:
    df_print: paged
date: "2026-04-13"
---

```{r setup, include=FALSE}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, tidyverse, rlist, modelsummary,
  haven, corrplot, effectsize, emmeans, 
  lmtest, lfe, stargazer, scales, tigris, sf, fixest,
  ggplot2, readr, fixest, arrow
)
```

The goal of this script is to create some necessary variables and estimate the impact of treatment on daily water consumption using several regressopn specfications (different combinations of fixed effects, different time periods, winsorized and trimmed regressions, dropping observations based on prespecified rules). This is part of an RCT design where treated households were given information on their water consumption and pricing depending on which treatment arm they were placed in. There are three separate treatment arms: SC, SPC and RPC.

We look at three separate time windows: 
1. Full: December 2023 - May 2025 is the pre-period and June 2025 - December 2025 is the post-period.
2. Summer: June - October 2024 is the pre-period and June - October 2025 is the post-period. Both periods include observations through October 31. The post-period begins on the date a household receives its first notification and therefore varies
across households. The pre-period begins on the corresponding date in 2024.
3. Six months: December 2024 - May 2025 is the pre-period and June - October 2025 is the post-period. For each household, the pre-period begins on the day they receive their first notification minus 180 days. The post-period ends on the day they receive their first notification plus 180 days.

All winsorization and trimming are done after restricting the sample to the relevant time periods for that specific model. Winsorization is done at the top 0.1%, 0.5% and 1% at the observation level. Trimming is done by removing the top 0.1%, 0.5% and 1% of households based on average pre-consumption which is the average daily water usage per household in the pre-period depending on the specific model.

We also look at some specifications having removed the daily water consumption values that are zero or negative where the latter is due to a meter resetting issue. 


# Load data
```{r}
# Dataset was saved as parquet to optimize space
merged_treat_clean <- read_parquet("~/projects/eel/westminster/use_data/price_experiment/analysis_files/daily_consumption_with_treatment.parquet")
```


# Function for var creation
```{r}
# Function for dummy vars

create_dummy_variables <- function(data, column_name) {
  result_data <- data.frame(data)
  if (!is.factor(result_data[[column_name]])) {
    result_data[[column_name]] <- as.factor(result_data[[column_name]])
  }
  
  dummy_levels <- levels(result_data[[column_name]])
  
  dummy_names <- c()
  for (level in dummy_levels) {
    dummy_name <- paste0(column_name, "_", make.names(level))
    dummy_names <- append(dummy_names, dummy_name)
    result_data[[dummy_name]] <- as.integer(result_data[[column_name]] == level)
  }
  
  return(list(result_data, dummy_names))
}

```

# Creating vars for regressions

Households are grouped into different billing cycles. The treatment period (during which households received notifications about their water usage) was between June-October 2025. Therefore, each household received the first notification on a different day in June based on their billing cycle. The post treatment period variable is created below based on this first notification date.

```{r}
cycle_notif_mappings <- list()
for (cyc in unique(merged_treat_clean_1$cycle)) {
  data_filt <- merged_treat_clean_1 %>% filter(cycle == cyc)
  cycle_notif_mappings[[paste(cyc)]] <- unique(na.omit(data_filt$first_notification))
}

notification_df <- data.frame(
  cycle = as.integer(names(cycle_notif_mappings)),
  replacement_date = as.Date(unlist(cycle_notif_mappings), origin = "1970-01-01"),
  stringsAsFactors = FALSE
)
rownames(notification_df) <- NULL


# Date of first notification for treated groups
merged_treat_clean_2 <- merged_treat_clean %>%
  left_join(notification_df, by = "cycle") %>%
  mutate(
    first_notification_analysis = case_when(
      treatment == "Control" ~ replacement_date,
      TRUE ~ first_notification
    )
  ) %>%
  select(-replacement_date)

# Creating post variable depending on first notification date
consumption_interval_panel <- merged_treat_clean_2 %>%
  arrange(acct, date) %>%
  group_by(acct) %>%
  mutate(
    # Ensuring that var is in the correct format
    treatment_time = as.POSIXct(first_notification_analysis),
    post = case_when(
      is.na(date) | is.na(treatment_time) ~ NA_real_,
      date < treatment_time ~ 0, 
      date >= treatment_time ~ 1, # the date on which first notif is received is assumed to be post
      TRUE ~ NA_real_
    )) %>%
  ungroup()

# Checking for missing data
consumption_interval_panel %>%
  summarise(
    na_post = sum(is.na(post)),
    na_treatment = sum(is.na(treatment)),
    na_daily_usage_clean = sum(is.na(daily_usage_clean))
  ) #212358 obs in daily_usage_clean are missing

missing_by_day <- consumption_interval_panel %>%
  filter(is.na(daily_usage_clean)) %>%
  count(date, sort = TRUE)

consumption_interval_panel_1 <- consumption_interval_panel %>%
  filter(
    !is.na(daily_usage_clean)
  )


# Fixed effects
consumption_interval_panel_1 <- consumption_interval_panel_1 %>%
  mutate(
    day_fe = date)

# Treatment dummies
dummy_output <- create_dummy_variables(consumption_interval_panel_1, "treatment")
consumption_interval_panel_1 <- dummy_output[[1]]
treatment_dummy_names <- dummy_output[[2]]

rm(dummy_output)
gc()


# Interaction variables needed for regressions
consumption_interval_panel_1 <- consumption_interval_panel_1 %>%
  mutate(
    treat = as.integer(treatment != "Control"),
    treat_post = treat * post
  )

# Treatment-specific post interactions
for (v in treatment_dummy_names) {
  if (v != "treatment_Control") {
    new_name <- paste0(v, "_post")
    consumption_interval_panel_1[[new_name]] <- consumption_interval_panel_1[[v]] * consumption_interval_panel_1$post
  }
}

# Regression-ready panel with relevant variables
consump_panel <- consumption_interval_panel_1 %>%
  select(
    meter_id, acct, treatment, post, first_notification_analysis,
    treat, treat_post,
    all_of(treatment_dummy_names),
    ends_with("_post"),
    date, day_fe, 
    daily_usage, daily_usage_clean,
  )

# Removing datasets to optimize memory usage
rm(consumption_interval_panel, consumption_interval_panel_1, data_filt, merged_treat_clean_1, merged_treat_clean_2)


```


# Daily water consumption regressions

## Functions for regressions

```{r}
# Functions cluster SEs at the HH (acct) level
# Function produce models with no FE, only HH FE, only date FE, then both HH and date FE

# For specifications that use daily_usage_clean 
run_did_specs <- function(rhs, data, cluster_var = "acct") {
  feols(
    as.formula(paste0(
      "daily_usage_clean ~ ", rhs,
      " | sw(0, acct, day_fe, acct + day_fe)"
    )),
    data = data,
    cluster = as.formula(paste0("~", cluster_var))
  )
}

# For slightly more complex specifications
run_did_specs_other <- function(lhs, rhs, data, cluster_var = "acct") {
  feols(
    as.formula(paste0(
      lhs, " ~ ", rhs,
      " | sw(0, acct, day_fe, acct + day_fe)"
    )),
    data = data,
    cluster = as.formula(paste0("~", cluster_var))
  )
}

# Function to view all 4 specifications at once
view_did_specs <- function(spec) {
  fe_labels <- c("No FE", "Acct FE", "Day FE", "Acct + Day FE")
  for (i in 1:4) {
    cat("\n====", fe_labels[i], "====\n")
    print(summary(spec[[i]]))
  }
}

# Winsorized
winsorize_top <- function(x, p) {
  threshold <- quantile(x, 1 - p, na.rm = TRUE)
  pmin(x, threshold)
}

# Trimming function — drops HHs above the threshold based on avg HH preconsumption
trim_top_hh <- function(data, hh_stats, p) {
  threshold <- quantile(hh_stats$avg_pre_usage, 1 - p, na.rm = TRUE)
  keep_accts <- hh_stats %>% filter(avg_pre_usage <= threshold) %>% pull(acct)
  data %>% filter(acct %in% keep_accts)
}

```


# Functions for saving output

```{r}
save_did_etable <- function(models, file, title = NULL) {
  etable(
    models,
    tex = TRUE,
    file = file,
    replace = TRUE,
    title = title,
    depvar = TRUE,
    
    dict = c(
      daily_usage_clean = "Daily Consumption",
      "(Intercept)" = "Constant",
      log_daily_usage_no_0 = "Log Consumption",
      log_daily_usage_no_neg = "Log (Consumption + 1)",
      arcsinh_daily_usage_no_neg = "arcsinh(consumption)",
      daily_usage_w0.1 = "Daily Consumption",
      daily_usage_w0.5 = "Daily Consumption",
      daily_usage_w1 = "Daily Consumption",
      daily_usage_summer_w0.1 = "Daily Consumption",
      daily_usage_summer_w0.5 = "Daily Consumption",
      daily_usage_summer_w1 = "Daily Consumption",
      treat_post = "Treatment × Post",
      treatment_SC_post = "SC × Post",
      treatment_SPC_post = "SPC × Post",
      treatment_RPC_post = "RPC × Post",
      acct = "HH FE",
      day_fe = "Date FE"
    ),
    se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10)
  )
}

save_all_did_tables <- function(model_list, output_dir = "~/projects/eel/westminster/zarrin/code_new/price_salience/analysis/analysis_zarrin/reg_tables") {
  if (!dir.exists(output_dir)) {
    dir.create(output_dir, recursive = TRUE)
  }
  for (nm in names(model_list)) {
    save_did_etable(
      models = model_list[[nm]],
      file = file.path(output_dir, paste0(nm, ".tex")),
      title = nm
    )
  }
}
```


## Dec2023-Dec2025
```{r}

spec1_dec2023_2025 <- run_did_specs(
  rhs = "treat_post",
  data = consump_panel
)

spec2_dec2023_2025 <- run_did_specs(
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel
)

view_did_specs(spec1_dec2023_2025)
view_did_specs(spec2_dec2023_2025)
```


### Winsorized

```{r}
consump_panel <- consump_panel %>%
  mutate(daily_usage_w0.1 = winsorize_top(daily_usage_clean, 0.001),
         daily_usage_w0.5 = winsorize_top(daily_usage_clean, 0.005),
         daily_usage_w1 = winsorize_top(daily_usage_clean, 0.01))

# regressions
spec1_dec2023_2025_w0.1 <- run_did_specs_other("daily_usage_w0.1", "treat_post", consump_panel)
spec1_dec2023_2025_w0.5 <- run_did_specs_other("daily_usage_w0.5", "treat_post", consump_panel)
spec1_dec2023_2025_w1   <- run_did_specs_other("daily_usage_w1", "treat_post", consump_panel)

spec2_dec2023_2025_w0.1 <- run_did_specs_other("daily_usage_w0.1",
  "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  consump_panel)

spec2_dec2023_2025_w0.5 <- run_did_specs_other("daily_usage_w0.5",
  "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  consump_panel)

spec2_dec2023_2025_w1 <- run_did_specs_other("daily_usage_w1",
  "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  consump_panel)


```

### Trimmed

```{r}
# average pre-period consumption per HH
hh_avg_pre <- consump_panel %>%
  filter(post == 0) %>%
  group_by(acct) %>%
  summarise(avg_pre_usage = mean(daily_usage_clean, na.rm = TRUE))

consump_panel_t0.1 <- trim_top_hh(consump_panel, hh_avg_pre, 0.001)
consump_panel_t0.5 <- trim_top_hh(consump_panel, hh_avg_pre, 0.005)
consump_panel_t1   <- trim_top_hh(consump_panel, hh_avg_pre, 0.01)

# regressions
spec1_dec2023_2025_t0.1 <- run_did_specs(rhs = "treat_post", data = consump_panel_t0.1)
spec1_dec2023_2025_t0.5 <- run_did_specs(rhs = "treat_post", data = consump_panel_t0.5)
spec1_dec2023_2025_t1 <- run_did_specs(rhs = "treat_post", data = consump_panel_t1)

spec2_dec2023_2025_t0.1 <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_t0.1)
spec2_dec2023_2025_t0.5 <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_t0.5)
spec2_dec2023_2025_t1   <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_t1)

# freeing up space
rm(consump_panel_t0.1, consump_panel_t0.5, consump_panel_t1)

```

### Removing all observations with 0 consumption

```{r}
# We look at log(daily consumption) in this case

consump_panel <- consump_panel %>%
  mutate(log_daily_usage_no_0 = if_else(daily_usage_clean > 0, log(daily_usage_clean), NA_real_))

spec1_dec2023_2025_no_0 <- run_did_specs_other("log_daily_usage_no_0", "treat_post", consump_panel)

spec2_dec2023_2025_no_0 <- run_did_specs_other("log_daily_usage_no_0", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel)
```

### Removing all observations with negative consumption

```{r}
# Check: daily_usage has positive, negative and 0 values. 

# We look at both log(daily consumption + 1) and arcsinh(daily consumption)

consump_panel <- consump_panel %>%
  mutate(log_daily_usage_no_neg = if_else(daily_usage >= 0, log(daily_usage_clean + 1), NA_real_),
         arcsinh_daily_usage_no_neg = if_else(daily_usage >= 0, asinh(daily_usage_clean), NA_real_))

# log spec
spec1_dec2023_2025_no_neg_log <- run_did_specs_other("log_daily_usage_no_neg", "treat_post", consump_panel)

spec2_dec2023_2025_no_neg_log <- run_did_specs_other("log_daily_usage_no_neg", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel)

# arcsinh spec
spec1_dec2023_2025_no_neg_arcsinh <- run_did_specs_other("arcsinh_daily_usage_no_neg", "treat_post", consump_panel)

spec2_dec2023_2025_no_neg_arcsinh <- run_did_specs_other("arcsinh_daily_usage_no_neg", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel)
```


### Saving output

```{r}
dec_2023_2025_did_specs <- list(
  spec1_dec2023_2025 = spec1_dec2023_2025,
  spec2_dec2023_2025 = spec2_dec2023_2025,
  # Winsorized
  spec1_dec2023_2025_w0.1 = spec1_dec2023_2025_w0.1,
  spec1_dec2023_2025_w0.5 = spec1_dec2023_2025_w0.5,
  spec1_dec2023_2025_w1   = spec1_dec2023_2025_w1,

  spec2_dec2023_2025_w0.1 = spec2_dec2023_2025_w0.1,
  spec2_dec2023_2025_w0.5 = spec2_dec2023_2025_w0.5,
  spec2_dec2023_2025_w1   = spec2_dec2023_2025_w1,
  
  # Top trimming
  spec1_dec2023_2025_t0.1 = spec1_dec2023_2025_t0.1,
  spec1_dec2023_2025_t0.5 = spec1_dec2023_2025_t0.5,
  spec1_dec2023_2025_t1   = spec1_dec2023_2025_t1,

  spec2_dec2023_2025_t0.1 = spec2_dec2023_2025_t0.1,
  spec2_dec2023_2025_t0.5 = spec2_dec2023_2025_t0.5,
  spec2_dec2023_2025_t1   = spec2_dec2023_2025_t1,
  
  # no 0s
  spec1_dec2023_2025_no_0 = spec1_dec2023_2025_no_0,
  spec2_dec2023_2025_no_0 = spec2_dec2023_2025_no_0,
  # no neg usages
  spec1_dec2023_2025_no_neg_log = spec1_dec2023_2025_no_neg_log,
  spec2_dec2023_2025_no_neg_log = spec2_dec2023_2025_no_neg_log,
  spec1_dec2023_2025_no_neg_arcsinh = spec1_dec2023_2025_no_neg_arcsinh,
  spec2_dec2023_2025_no_neg_arcsinh = spec2_dec2023_2025_no_neg_arcsinh
  
)
save_all_did_tables(
  model_list = dec_2023_2025_did_specs,
  output_dir = "~/projects/eel/westminster/output/pricing_experiment/reg_tex_files"
)

# freeing up space
rm(list = ls(pattern = "^spec"))

```


## Preperiod: June-Oct 2024, Postperiod: June-Oct 2025

```{r}
consump_panel_summer <- consump_panel %>%
  mutate(
    # Post-period start
    post_start = as.Date(first_notification_analysis),
    # Post-period end
    post_end = as.Date("2025-10-31"),
    # Pre-period start = exactly 1 year earlier
    pre_start = post_start %m-% years(1),
    # Pre-period end = Oct 31 2024
    pre_end = as.Date("2024-10-31")
  )

# Each HH should only contribute observations inside either window
consump_panel_summer <- consump_panel_summer %>%
  filter(
    (date >= pre_start & date <= pre_end) |
    (date >= post_start & date <= post_end)
  )
```


```{r}
spec1_summer2024_vs_2025 <- run_did_specs(
  rhs = "treat_post",
  data = consump_panel_summer
)

spec2_summer2024_vs_2025 <- run_did_specs(
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_summer
)

```


### Winsorized

```{r}
consump_panel_summer <- consump_panel_summer %>%
  mutate(daily_usage_summer_w0.1 = winsorize_top(daily_usage_clean, 0.001),
         daily_usage_summer_w0.5 = winsorize_top(daily_usage_clean, 0.005),
         daily_usage_summer_w1 = winsorize_top(daily_usage_clean, 0.01))

# regressions
spec1_summer2024_vs_2025_w0.1 <- run_did_specs_other("daily_usage_summer_w0.1", rhs = "treat_post", data = consump_panel_summer)
spec1_summer2024_vs_2025_w0.5 <- run_did_specs_other("daily_usage_summer_w0.5", rhs = "treat_post", data = consump_panel_summer)
spec1_summer2024_vs_2025_w1 <- run_did_specs_other("daily_usage_summer_w1", rhs = "treat_post", data = consump_panel_summer)

spec2_summer2024_vs_2025_w0.1 <- run_did_specs_other("daily_usage_summer_w0.1", 
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_summer
)
spec2_summer2024_vs_2025_w0.5 <- run_did_specs_other("daily_usage_summer_w0.5", 
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_summer
)
spec2_summer2024_vs_2025_w1 <- run_did_specs_other("daily_usage_summer_w1", 
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_summer
)
```



### Trimmed

```{r}
# average pre-period consumption per HH
hh_avg_pre_summer <- consump_panel_summer %>%
  filter(post == 0) %>%
  group_by(acct) %>%
  summarise(avg_pre_usage = mean(daily_usage_clean, na.rm = TRUE))

# trimmed datasets
consump_panel_summer_t0.1 <- trim_top_hh(consump_panel_summer, hh_avg_pre_summer, 0.001)
consump_panel_summer_t0.5 <- trim_top_hh(consump_panel_summer, hh_avg_pre_summer, 0.005)
consump_panel_summer_t1   <- trim_top_hh(consump_panel_summer, hh_avg_pre_summer, 0.01)

# regressions
spec1_summer2024_vs_2025_t0.1 <- run_did_specs(rhs = "treat_post", data = consump_panel_summer_t0.1)
spec1_summer2024_vs_2025_t0.5 <- run_did_specs(rhs = "treat_post", data = consump_panel_summer_t0.5)
spec1_summer2024_vs_2025_t1 <- run_did_specs(rhs = "treat_post", data = consump_panel_summer_t1)

spec2_summer2024_vs_2025_t0.1 <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_summer_t0.1)
spec2_summer2024_vs_2025_t0.5 <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_summer_t0.5)
spec2_summer2024_vs_2025_t1   <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_summer_t1)
```


### Removing all observations with 0 consumption

```{r}
spec1_summer2024_vs_2025_no_0 <- run_did_specs_other("log_daily_usage_no_0", "treat_post", consump_panel_summer)

spec2_summer2024_vs_2025_no_0 <- run_did_specs_other("log_daily_usage_no_0", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_summer)
```

### Removing all observations with negative consumption

```{r}

# log spec
spec1_summer2024_vs_2025_no_neg_log <- run_did_specs_other("log_daily_usage_no_neg", "treat_post", consump_panel_summer)

spec2_summer2024_vs_2025_no_neg_log <- run_did_specs_other("log_daily_usage_no_neg", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_summer)

# arcsinh spec
spec1_summer2024_vs_2025_no_neg_arcsinh <- run_did_specs_other("arcsinh_daily_usage_no_neg", "treat_post", consump_panel_summer)

spec2_summer2024_vs_2025_no_neg_arcsinh <- run_did_specs_other("arcsinh_daily_usage_no_neg", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_summer)
```



### Saving output

```{r}
summer2024_vs_2025_did_specs <- list(
  spec1_summer2024_vs_2025 = spec1_summer2024_vs_2025,
  spec2_summer2024_vs_2025 = spec2_summer2024_vs_2025,

  # Winsorized
  spec1_summer2024_vs_2025_w0.1 = spec1_summer2024_vs_2025_w0.1,
  spec1_summer2024_vs_2025_w0.5 = spec1_summer2024_vs_2025_w0.5,
  spec1_summer2024_vs_2025_w1   = spec1_summer2024_vs_2025_w1,

  spec2_summer2024_vs_2025_w0.1 = spec2_summer2024_vs_2025_w0.1,
  spec2_summer2024_vs_2025_w0.5 = spec2_summer2024_vs_2025_w0.5,
  spec2_summer2024_vs_2025_w1   = spec2_summer2024_vs_2025_w1,
  
  # Top trimming
  spec1_summer2024_vs_2025_t0.1 = spec1_summer2024_vs_2025_t0.1,
  spec1_summer2024_vs_2025_t0.5 = spec1_summer2024_vs_2025_t0.5,
  spec1_summer2024_vs_2025_t1   = spec1_summer2024_vs_2025_t1,

  spec2_summer2024_vs_2025_t0.1 = spec2_summer2024_vs_2025_t0.1,
  spec2_summer2024_vs_2025_t0.5 = spec2_summer2024_vs_2025_t0.5,
  spec2_summer2024_vs_2025_t1   = spec2_summer2024_vs_2025_t1
)

save_all_did_tables(
  model_list = summer2024_vs_2025_did_specs,
  output_dir = "~/projects/eel/westminster/zarrin/code_new/price_salience/analysis/analysis_zarrin/reg_tables"
)

# Saving the new tables
summer2024_vs_2025_did_specs_1 <- list(
  spec1_summer2024_vs_2025_no_0 = spec1_summer2024_vs_2025_no_0,
  spec2_summer2024_vs_2025_no_0 = spec2_summer2024_vs_2025_no_0,
  spec1_summer2024_vs_2025_no_neg_log = spec1_summer2024_vs_2025_no_neg_log,
  spec2_summer2024_vs_2025_no_neg_log = spec2_summer2024_vs_2025_no_neg_log,
  spec1_summer2024_vs_2025_no_neg_arcsinh = spec1_summer2024_vs_2025_no_neg_arcsinh,
  spec2_summer2024_vs_2025_no_neg_arcsinh = spec2_summer2024_vs_2025_no_neg_arcsinh)

save_all_did_tables(
  model_list = summer2024_vs_2025_did_specs_1,
  output_dir = "~/projects/eel/westminster/output/pricing_experiment/reg_tex_files"
)

# freeing up space
rm(list = ls(pattern = "^spec"))
rm(list = ls(pattern = "^consump_panel_summer"), hh_avg_pre, hh_avg_pre_summer)
```



## 6 months pre-post: Dec 2024-2025

```{r}
consump_panel_6_mths <- consump_panel %>%
  mutate(
    pre_start  = first_notification_analysis - days(180),
    pre_end    = first_notification_analysis - days(1),
    post_start = first_notification_analysis,
    post_end   = first_notification_analysis + days(180)
  )

# Keeping only observations inside the symmetric window
consump_panel_6_mths <- consump_panel_6_mths %>%
  filter(
    date >= pre_start &
    date <= post_end
  )

spec1_six_mths <- run_did_specs(
  rhs = "treat_post",
  data = consump_panel_6_mths_1
)

spec2_six_mths <- run_did_specs(
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_6_mths_1
)
```

### Winsorized

```{r}
consump_panel_6_mths_w0.1 <- consump_panel_6_mths_1 %>%
  mutate(daily_usage_clean = winsorize_top(daily_usage_clean, 0.001))
consump_panel_6_mths_w0.5 <- consump_panel_6_mths_1 %>%
  mutate(daily_usage_clean = winsorize_top(daily_usage_clean, 0.005))
consump_panel_6_mths_w1 <- consump_panel_6_mths_1 %>%
  mutate(daily_usage_clean = winsorize_top(daily_usage_clean, 0.01))

# regressions
spec1_6_mths_w0.1 <- run_did_specs(rhs = "treat_post", data = consump_panel_6_mths_w0.1)
spec1_6_mths_w0.5 <- run_did_specs(rhs = "treat_post", data = consump_panel_6_mths_w0.5)
spec1_6_mths_w1 <- run_did_specs(rhs = "treat_post", data = consump_panel_6_mths_w1)

spec2_6_mths_w0.1 <- run_did_specs(
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_6_mths_w0.1
)
spec2_6_mths_w0.5 <- run_did_specs(
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_6_mths_w0.5
)
spec2_6_mths_w1 <- run_did_specs(
  rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post",
  data = consump_panel_6_mths_w1
)

# freeing up space
rm(list = ls(pattern = "^consump_panel_6_mths_w"), consump_panel_6_mths)
```

### Trimmed

```{r}
# average pre-period consumption per HH
hh_avg_pre_6_mths <- consump_panel_6_mths %>%
  filter(post == 0) %>%
  group_by(acct) %>%
  summarise(avg_pre_usage = mean(daily_usage_clean, na.rm = TRUE))

# trimmed datasets
consump_panel_6_mths_t0.1 <- trim_top_hh(consump_panel_6_mths, hh_avg_pre_6_mths, 0.001)
consump_panel_6_mths_t0.5 <- trim_top_hh(consump_panel_6_mths, hh_avg_pre_6_mths, 0.005)
consump_panel_6_mths_t1   <- trim_top_hh(consump_panel_6_mths, hh_avg_pre_6_mths, 0.01)

# regressions
spec1_6_mths_t0.1 <- run_did_specs(rhs = "treat_post", data = consump_panel_6_mths_t0.1)
spec1_6_mths_t0.5 <- run_did_specs(rhs = "treat_post", data = consump_panel_6_mths_t0.5)
spec1_6_mths_t1 <- run_did_specs(rhs = "treat_post", data = consump_panel_6_mths_t1)

spec2_6_mths_t0.1 <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_6_mths_t0.1)
spec2_6_mths_t0.5 <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_6_mths_t0.5)
spec2_6_mths_t1   <- run_did_specs(rhs = "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_6_mths_t1)
```

### Removing all observations with 0 consumption
```{r}

spec1_6_mths_no_0 <- run_did_specs_other("log_daily_usage_no_0", "treat_post", consump_panel_6_mths)

spec2_6_mths_no_0 <- run_did_specs_other("log_daily_usage_no_0", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_6_mths)
```

### Removing all observations with negative consumption

```{r}
# log spec
spec1_6_mths_no_neg_log <- run_did_specs_other("log_daily_usage_no_neg", "treat_post", consump_panel_6_mths)

spec2_6_mths_no_neg_log <- run_did_specs_other("log_daily_usage_no_neg", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_6_mths)

# arcsinh spec
spec1_6_mths_no_neg_arcsinh <- run_did_specs_other("arcsinh_daily_usage_no_neg", "treat_post", consump_panel_6_mths)

spec2_6_mths_no_neg_arcsinh <- run_did_specs_other("arcsinh_daily_usage_no_neg", "treatment_SC_post + treatment_SPC_post + treatment_RPC_post", data = consump_panel_6_mths)
```


### Saving output

```{r}
six_mths_did_specs <- list(
  spec1_6_mths = spec1_six_mths,
  spec2_6_mths = spec2_six_mths,

  # Winsorized
  spec1_6_mths_w0.1 = spec1_6_mths_w0.1,
  spec1_6_mths_w0.5 = spec1_6_mths_w0.5,
  spec1_6_mths_w1   = spec1_6_mths_w1,

  spec2_6_mths_w0.1 = spec2_6_mths_w0.1,
  spec2_6_mths_w0.5 = spec2_6_mths_w0.5,
  spec2_6_mths_w1   = spec2_6_mths_w1,
  
  # Top trimming
  spec1_6_mths_t0.1 = spec1_6_mths_t0.1,
  spec1_6_mths_t0.5 = spec1_6_mths_t0.5,
  spec1_6_mths_t1   = spec1_6_mths_t1,

  spec2_6_mths_t0.1 = spec2_6_mths_t0.1,
  spec2_6_mths_t0.5 = spec2_6_mths_t0.5,
  spec2_6_mths_t1   = spec2_6_mths_t1
)

save_all_did_tables(
  model_list = six_mths_did_specs,
  output_dir = "~/projects/eel/westminster/zarrin/code_new/price_salience/analysis/analysis_zarrin/reg_tables"
)

# Saving the new tables
six_mths_did_specs_1 <- list(
  spec1_6_mths_no_0 = spec1_6_mths_no_0,
  spec2_6_mths_no_0 = spec2_6_mths_no_0,
  spec1_6_mths_no_neg_log = spec1_6_mths_no_neg_log,
  spec2_6_mths_no_neg_log = spec2_6_mths_no_neg_log,
  spec1_6_mths_no_neg_arcsinh = spec1_6_mths_no_neg_arcsinh,
  spec2_6_mths_no_neg_arcsinh = spec2_6_mths_no_neg_arcsinh)

save_all_did_tables(
  model_list = six_mths_did_specs_1,
  output_dir = "~/projects/eel/westminster/output/pricing_experiment/reg_tex_files"
)

# freeing up space
rm(list = ls(pattern = "^spec"))
rm(list = ls(pattern = "^consump_panel_6_mths"), hh_avg_pre_6_mths)
```